### 2017-05-30 paper.tex
Fix URL typography

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and Software Carpentry license their material under
the Creative Commons - Attribution license
(see https://creativecommons.org/licenses/by/2.0/).
This allows people to share and adapt material for any purpose,
even commercial ones,
without asking permissions as long as they continue to share the content in a similar manner.

>>>>

Before re-using content,
make sure to check that the lesson is licensed in an open manner.
Both Programming Historian and Software Carpentry license their material under
the Creative Commons - Attribution license\footnote{\url{https://creativecommons.org/licenses/by/2.0/}}.
This allows people to share and adapt material for any purpose,
even commercial ones,
without asking permissions as long as they continue to share the content in a similar manner.
